---
title: "NFL QB Case Study"
author: "Cornelius Williams"
date: "2023-05-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions to be answered

1. Does it take a good defense to win the Superbowl?
1. Does it take a great quarterback play to win the Superbowl?
1. Does it matter which round a team drafts a quarterback?
1. Can a team draft a quarterback in a later round and pair them with a good defense to win?
1. Which rounds are quarterbacks that make it to the playoffs and Superbowl drafted in?

### In my data analysis case study I set out to answer these questions by gathering data over a twenty year period that included information listed below.
* NFL defensive stats 
* Quarterback regular season and playoff stats 
* Superbowl team and quarterback participants 
* Rounds that each quarterback was drafted 



```{r loading packages for gathering data and saving to local file, message=FALSE, warning=FALSE, include=FALSE}
#install.packages("rvest", repos = "http://cran.us.r-project.org")
install.packages("tidyverse", repos = 'http://cran.us.r-project.org')
#install.packages("xml2", repos = "http://cran.us.r-project.org")
install.packages("readxl", repos = "http://cran.us.r-project.org")
#install.packages("xlsx", repos = "http://cran.us.r-project.org")


#library(rvest)
library(tidyverse)
#library(xml2)
library(readxl)
#library(xlsx)


```
```{r scrape website for data, eval=FALSE, include=FALSE, paged.print=FALSE}
#scrape defensive stats for multiple seasons and saved html to local folder
setwd("C:/Users/Darnell W/Desktop/Portfolio/R practice/NFL Project/defense")
for(i in 2002:2021){
  defense_url <- read_html(paste0("https://www.pro-football-reference.com/years/",i,"/opp.htm"))
  defense_stats <- defense_url %>%
    write_html(paste0("defense",i,".HTML"))
}

#scrape passing stats multiple seasons and saved html to local folder
setwd("C:/Users/Darnell W/Desktop/Portfolio/R practice/NFL Project/passing")
for(i in 2002:2021){
  passing_url <- read_html(paste0("https://www.espn.com/nfl/stats/player/_/season/",i,"/seasontype/3/table/passing/sort/QBRating/dir/desc"))
  passing_stats <- passing_url %>%
    write_html(paste0("passing",i,".HTML"))
}

#scrape regualar season passing stats multiple seasons and saved html to local folder
setwd("C:/Users/Darnell W/Desktop/Portfolio/R practice/NFL Project/reg_season")
for(i in 2002:2021){
  regsea_url <- read_html(paste0("https://www.espn.com/nfl/stats/player/_/season/",i,"/seasontype/2/table/passing/sort/QBRating/dir/desc"))
  regsea_stats <- regsea_url %>%
    write_html(paste0("regseason",i,".HTML"))
}

#scrape draft stats multiple seasons and saved html to local folder
setwd("C:/Users/Darnell W/Desktop/Portfolio/R practice/NFL Project/draft")
for (i in 1986:2021) {
  draft_url <- read_html(paste0("https://www.pro-football-reference.com/years/",i,"/draft.htm"))
  draft_stats <- draft_url %>%
    write_html(paste0("draft",i,".HTML"))
}

#scrape superbowl teams and saved html to local folder
setwd("C:/Users/Darnell W/Desktop/Portfolio/R practice/NFL Project/superbowl")
sb_url <- read_html("https://en.wikipedia.org/wiki/List_of_Super_Bowl_starting_quarterbacks")
superbowl <- sb_url %>%
  write_html("suberbowl.HTML")
}

#scrape  team abbreviations and saved html to local folder
setwd("C:/Users/Darnell W/Desktop/Portfolio/R practice/NFL Project/Team_abbreviations")
teamAbr_url < read_html("https://en.wikipedia.org/wiki/Wikipedia:WikiProject_National_Football_League/National_Football_League_team_abbreviations")
Teams <- teamAbr_url %>%
  write_html("Team_abreviations.csv")
}
```
```{r load data from local files into dataframes, eval=FALSE, include=FALSE}

#Use For loop to take locally save files and extract tables to make data frame
setwd("C:/Users/Darnell W/Desktop/Portfolio/R practice/NFL Project/playoffs")
file_playoffs <- list.files()
QBPlayoffs <- list()

for(file in file_playoffs){
  read_html(file) -> playoffs
  
  
  playoffs %>% 
    html_nodes("table") %>% 
    html_table() -> playoff_stats
  
  playoff_stats %>% 
    as.data.frame() -> playoff_stats
  playoff_stats$Year <- file
  
  
  
  QBPlayoffs[[length(QBPlayoffs) +1]] <- playoff_stats
}


QBPlayoffs1 <- bind_rows(QBPlayoffs[1:4], QBPlayoffs[6], QBPlayoffs[8], QBPlayoffs[12:14], 
                         QBPlayoffs[17:18], QBPlayoffs[21] ) #Combine all the dataframes into one.

QBPlayoffs2 <- bind_rows(QBPlayoffs[5], QBPlayoffs[7], QBPlayoffs[9:11], QBPlayoffs[15:16], 
                         QBPlayoffs[19], QBPlayoffs[20] ) #Combine all the dataframes into one.

QBPlayoffs2$YDS = as.integer(QBPlayoffs2$YDS) #change the data type in the YDS column to match the same column in QBPlayoffs1
QBPlayoffs <- rbind(QBPlayoffs1, QBPlayoffs2) #combine data frames to prepare for cleaning 

#Remove data frames and list
rm(QBPlayoffs1, QBPlayoffs2, playoff_stats, playoffs)

#Use For loop to take locally save files and extract tables to make data frame
setwd("C:/Users/Darnell W/Desktop/Portfolio/R practice/NFL Project/reg_season")
file_regsea <- list.files()

Regsea <- list()

for(file in file_regsea){
  read_html(file) -> passing
  
  passing %>% 
    html_nodes("table") %>% 
    html_table() -> regsea_stats
  #drafts
  regsea_stats %>% 
    as.data.frame() -> regsea_stats
  regsea_stats$Year <- file
  
  Regsea[[length(Regsea) +1]] <- regsea_stats
  
  
}
Regsea <- bind_rows(Regsea) 

#Remove data frames and list
rm(regsea_stats, passing)

#Use For loop to take locally save files and extract tables to make data frame
setwd("C:/Users/Darnell W/Desktop/Portfolio/R practice/NFL Project/draft")
file_draft <- list.files()
Draft <- list()

for(file in file_draft){
  read_html(file) -> picks
  
  picks %>% 
    html_nodes("#drafts") %>% 
    html_table() -> draft_stats
  
  draft_stats %>% 
    as.data.frame() -> draft_stats
    draft_stats$Year <- file
  
  Draft[[length(Draft) +1]] <- draft_stats
  
  
}
Draft <- bind_rows(Draft) #Combine all the dataframes into one.

#Remove data frames and list
rm(picks, draft_stats)

#Use For loop to take locally save files and extract tables to make data frame
setwd("C:/Users/Darnell W/Desktop/Portfolio/R practice/NFL Project/defense")
file_defense <- list.files()
Defense <- list()

for(file in file_defense){
  read_html(file) -> defense
  
  defense %>% 
    html_nodes("#team_stats") %>% 
    html_table() -> defense_stats
  
  defense_stats %>% 
    as.data.frame() -> defense_stats
  defense_stats$Year <- file
  
  Defense[[length(Defense) +1]] <- defense_stats
  
}

Defense <- bind_rows(Defense) #Combine all the dataframes into one.

#Remove data frames and list
rm(defense, defense_stats)


#Read local csv file in and converted into data frame
setwd("C:/Users/Darnell W/Desktop/Portfolio/R practice/NFL Project/Team_abreviations")
Teams <- read.csv("C:/Users/Darnell W/Desktop/Portfolio/R practice/NFL Project/Team_abreviations/teams.csv")

setwd("C:/Users/Darnell W/Desktop/Portfolio/R practice/NFL Project/superbowl")
file_superbowl <- list()

read_html("suberbowl.HTML") -> sb
sb %>% 
  html_nodes("table") %>%
  html_table(fill = TRUE) -> sb

# Convert list to dataframe using data.frame()
sb <- data.frame(sb[[2]])
```
```{r cleaning the dataframe and merging dataframes into single dataframe, eval=FALSE, include=FALSE}
#---------------Cleaning'Teams"data frame-------------------------------------------------------------------------
Teams <- Teams %>% 
  select(-ID, -Conference, -Division)

Teams <- rename(Teams, team_code=Abbreviation)
Teams <- rename(Teams, team=Name)


#----------------Cleaning "Defense"data frame-----------------------------------------------------------------------
Defense_clean <- Defense



#Removed characters and punctuation from Year column
Defense_clean$Year <- gsub("defense", "", Defense_clean$Year) 
Defense_clean$Year <- gsub(".HTML", "", Defense_clean$Year)



#Renaming some of the column names
Defense_clean <- dplyr::rename(Defense_clean, team=Var.2, 
                        defense_rank=Var.1, year=Year)

# cleaning data frame by removing unecessary rows using value in the row
Defense_clean <- Defense_clean[!(Defense_clean$defense_rank == "Rk"),]
Defense_clean <- Defense_clean[!(Defense_clean$defense_rank == ""), ]

#Modify strings to proper names
Defense_clean <- Defense_clean %>%  
  mutate(team = str_replace(team, "Football Team", "Commanders")) %>% 
  mutate(team = str_replace(team, "Redskins", "Commanders")) %>%
  mutate(team = str_replace(team, "Oakland", "Las Vegas")) %>%
  mutate(team = str_replace(team, "St. Louis", "Los Angeles")) %>%
  mutate(team = str_replace(team, "San Diego", "Los Angeles")) %>%
  mutate(team = str_replace(team, "Tampa Bay", "Tampa Bay"))

#Defense_clean<-left_join(Defense_clean, Teams, by = "team")


#Remove columns
Defense_clean[, 3:28] <- (NULL)

#Changed the column classes of df
Defense_clean <- type.convert(Defense_clean, as.is = TRUE)

#----------------Cleaning "Draft"data frame-----------------------------------------------------------------------
Draft_clean <- Draft

Draft_clean <- rename(Draft_clean, round_drafted=Var.1, pick=Var.2, 
                      player=Var.4, position=Var.5) #Renaming some of the column names

#Removed characters and punctuation from Year column
Draft_clean$player <- gsub(" HOF", "", Draft_clean$player)
Draft_clean$player <- gsub("Michael Vick", "Mike Vick", Draft_clean$player)
Draft_clean$player <- gsub("Mitchell Trubisky", "Mitch Trubisky", Draft_clean$player)
Draft_clean$player <- sub("Robert Griffin III", "Robert Griffin", Draft_clean$player)

#Remove whitespace from column
Draft_clean$player <- trimws(Draft_clean$player, which = "both")


#cleaning data frame by removing unecessary rows using value in the row
Draft_clean <- Draft_clean[(Draft_clean$position == "QB"),]

#Removed columns that aren't need for analysis

#Changing NAs to Undrafted
Draft_clean[is.na(Draft_clean)] <- "Undrafted"


Draft_clean <- Draft_clean %>% 
  select(-c(position:Var.29, Var.3, pick))


#Changed the column classes of df
Draft_clean <- type.convert(Draft_clean, as.is = TRUE)


#----------------Cleaning "Suberbowl"data frame-----------------------------------------------------------------------
#Removed all special characters from dataframe for cleaning
sb_clean<-sb %>%
  mutate(across(everything(), ~gsub("[[:punct:]]", "", .x)))

# Removed the last character from Team and Team.1 column, for cleaning
sb_clean$Team <- str_sub(sb_clean$Team, end = -2)
sb_clean$Team.1 <- str_sub(sb_clean$Team.1, end = -2)

# Modifying strings for cleaning
sb_clean$Winning.QB <-gsub("MVP","",as.character(sb_clean$Winning.QB ))
sb_clean$Season <- gsub("AFLNFL", "", sb_clean$Season)

#Changing column strings
sb_clean <- sb_clean %>%  
  select(-Super.Bowl) %>% 
  mutate(Team = str_replace(Team, "Redskins", "Commanders")) %>%
  mutate(Team.1 = str_replace(Team.1, "Redskins", "Commanders")) %>%
  mutate(Team = str_replace(Team, "Oakland", "Las Vegas")) %>%
  mutate(Team.1 = str_replace(Team.1, "Oakland", "Las Vegas")) %>%
  mutate(Team = str_replace(Team, "St. Louis", "Los Angeles")) %>%
  mutate(Team.1 = str_replace(Team.1, "St. Louis", "Los Angeles")) %>%
  mutate(Team = str_replace(Team, "San Diego", "Los Angeles")) %>%
  mutate(Team.1 = str_replace(Team.1, "San Diego", "Los Angeles")) %>%
  mutate(Team = str_replace(Team, "Tampa Bay", "Tampa Bay")) %>% 
  mutate(Team.1 = str_replace(Team.1, "Tampa Bay", "Tampa Bay")) %>% 
  mutate(superbowlqb = ifelse(!is.na(sb_clean$Winning.QB), 'yes', 'yes')) %>% 
  rename(Winning_team=Team, Losing_team=Team.1, Year=Season, Winning_qb=Winning.QB, Losing_qb=Losing.QB)
  

#Deleted row 57 for cleaning 
sb_clean <- sb_clean[-58,]


#Removed Suberbowls before 2001
sb_clean <-sb_clean[sb_clean$Year > "2001"  & sb_clean$Year < "2022",]



#Made new DF where to converted two colomns to rows to easier join dfs
sb_clean <- data.frame(year = c(sb_clean[,"Year"], sb_clean[,"Year"]),
                               player = c(sb_clean[,"Winning_qb"], sb_clean[,"Losing_qb"]),
                                superbowl = c(sb_clean[,"superbowlqb"], sb_clean[,"superbowlqb"]),
                              team = c(sb_clean[,"Winning_team"], sb_clean[,"Losing_team"]))

#adding new column
sb_clean <- sb_clean%>%
  mutate(sb_winner=c("yes"))
  sb_clean[21:40, 5] = "no"

#Changed the column classes of df
sb_clean <- type.convert(sb_clean, as.is = TRUE)

#combining dfs
sb_clean <- left_join(sb_clean, Draft_clean, by = "player")

#Changing NA's to Undrafted
sb_clean[is.na(sb_clean)] <- "Undrafted"


#-----------------Cleaning "Playoff"data frame------------------------------------------------------------------------------------
playoff_clean <- QBPlayoffs

#Remove columns
playoff_clean[, 4:16] <- (NULL)
playoff_clean[, 1] <- (NULL)

#Modify column
playoff_clean$Year <-gsub(".html", "", playoff_clean$Year)

#cleaning data frame by removing unecessary rows using value in the row
playoff_clean <- playoff_clean[(playoff_clean$POS == "QB"),]

#create new column Team_code
playoff_clean <- playoff_clean %>% 
  mutate(team_code = str_extract(playoff_clean$Name,"[A-Z/]+$")) %>% 
  dplyr::rename(playoff_rtg=RTG, year=Year, player=Name)

#Trimmed the Name column to remove the Team_code from the name
playoff_clean$player <- trimws(playoff_clean$player, whitespace = "[A-Z/]+", which = "right")


#Fixed one record where "III"needed to be added to one column and removed from another
playoff_clean$team_code <- sub("IIIWSH", "WSH", playoff_clean$team_code)
playoff_clean$player <- sub("Robert Griffin III", "Robert Griffin", playoff_clean$player)

#Removing white space from column
playoff_clean$player <- trimws(playoff_clean$player, which = "both")

#Changing column strings
playoff_clean <- playoff_clean %>%  
  mutate(team_code = str_replace(team_code, "OAK", "LV")) %>%
  mutate(team_code = str_replace(team_code, "STL", "LAR")) %>%
  mutate(team_code = str_replace(team_code, "SD", "LAR")) %>% 
  mutate(team_code = str_replace(team_code, "WSH", "WAS")) 
  




#joining data frames
playoff_clean<-left_join(playoff_clean, Teams, by = "team_code")

#removed columns
playoff_clean<-playoff_clean %>% 
  select(-team_code, -POS)

#Changed the column classes of df
playoff_clean <- type.convert(playoff_clean, as.is = TRUE)


#-----------------Cleaning "Regular Season"data frame-----------------------------------------------------------------
Regsea_clean<-Regsea

#create new column Team_code
Regsea_clean <- Regsea_clean %>% 
  mutate(team_code = str_extract(Regsea_clean$Name,"[A-Z/]+$")) %>% 
  dplyr::rename(player=Name, year=Year, rtg=RTG)

#Trimmed the Name column to remove the Team_code from the name
Regsea_clean$player <- trimws(Regsea_clean$player, whitespace = "[A-Z/]+", which = "right")


#Fixed one record where "III"needed to be added to one column and removed from another
Regsea_clean$team_code <- sub("IIIWSH", "WSH", Regsea_clean$team_code)
Regsea_clean$team_code <- sub("IIICLE", "CLE", Regsea_clean$team_code)
Regsea_clean$player <- sub("Robert Griffin III", "Robert Griffin", Regsea_clean$player)


#Removing white space from column	
Regsea_clean$player <- trimws(Regsea_clean$player, which = "both")

#Changing column strings
Regsea_clean <- Regsea_clean %>%  
  mutate(team_code = str_replace(team_code, "OAK", "LV")) %>%
  mutate(team_code = str_replace(team_code, "STL", "LAR")) %>%
  mutate(team_code = str_replace(team_code, "SD", "LAC")) %>% 
  mutate(team_code = str_replace(team_code, "WSH", "WAS")) 

#Removed characters and punctuation from Year column
Regsea_clean$year <- gsub("regseason", "", Regsea_clean$year) 
Regsea_clean$year <- gsub(".HTML", "", Regsea_clean$year)




#Changed the column classes of df
Regsea_clean <- type.convert(Regsea_clean, as.is = TRUE)

#Remove columns
Regsea_clean[, 3:16] <- (NULL)

Regsea_clean[, 1] <- (NULL)

#Combining dfs
Regsea_clean<-left_join(Regsea_clean, Teams, by = "team_code")
#removed columns
Regsea_clean<-Regsea_clean %>% 
  select(-team_code)
Regsea_clean<-left_join(Regsea_clean, Draft_clean, by = "player")
#Changing NA's to Undrafted
Regsea_clean[is.na(Regsea_clean)] <- "Undrafted"

Regsea_clean<-left_join(Regsea_clean, playoff_clean, by = c("player","team","year"))
Regsea_clean1<-left_join(Regsea_clean, Defense_clean, by = c("team","year"))


qb_final<-left_join(Regsea_clean1, sb_clean, by =c("player","year","team","round_drafted"))

qb_final <- qb_final %>% 
  mutate(sb_winner = ifelse(is.na(sb_winner), "no", sb_winner)) %>% 
  mutate(superbowl = ifelse(is.na(superbowl), "no", superbowl)) 

qb_final <- type.convert(qb_final, as.is = TRUE)
```


```{r loading Excel file into dataframe, echo=FALSE, message=FALSE, warning=FALSE}
setwd("C:/Users/Darnell W/Desktop/R_DASHBOARDS")
qb_final <- read_xlsx("C:/Users/Darnell W/Desktop/R_DASHBOARDS/flex_dashboards/qbfinal.xlsx")
```
### In this graph I used a boxplot to show the number of of quarterbacks that made the playoffs from 2002 to 2021.


* The results shown in this boxplot show that over the period of 2002 to 2021 that the majority of the quarterbacks that made it to the playoffs were drafted in the first round.

```{r boxplot, echo=FALSE, warning=FALSE}
qb_final %>% 
  filter(!is.na(playoff_rtg)) %>% 
  mutate(across(c('rtg'), round, 0)) %>% 
  group_by(round_drafted) %>% 
  ggplot(aes(x=round_drafted, y=rtg, color=round_drafted)) + 
  geom_boxplot() +
  geom_jitter() +
  labs(
    title= "Playoff Qaurterbacks",
    subtitle = "2002-2021",
    x = "Round Drafted",
    y = "QB Rating (Average)") +
  theme(legend.position = "none",
        plot.title=element_text(hjust=0.5, size = 10),
        plot.subtitle=element_text(hjust=0.5, size = 8))
```


### Here I used a lollipop chart to show how the average quarterback rating compare based on the round drafted.

* The results shown in this bar chart shows that even though quarterbacks drafted in the 1st and 2nd round were tie with the highest average quarterback rating, the next it's within five points of the next five positions.  

```{r QB rating dataframe, echo=FALSE, warning=FALSE}
rtg<-qb_final %>% 
  group_by(round_drafted) %>% 
  summarize(across(c("rtg"), ~ mean(.x, na.rm = TRUE))) %>% 
  arrange(desc(rtg))
```
```{r lollipop chart, echo=FALSE, warning=FALSE}
rtg %>%
  mutate(round_drafted = fct_reorder(round_drafted, rtg)) %>%
  mutate(across(c('rtg'), round, 0)) %>% 
  ggplot( aes(x=round_drafted, y=rtg, fill = round_drafted)) +
  geom_point(size = 6) +
  geom_segment(aes(x = round_drafted, xend = round_drafted, 
                   y = 0, yend = rtg), linewidth = 2.5) +
  scale_y_continuous(limits = c(0, 90), breaks = c(0, 15, 30, 45, 60, 75, 90)) +
  geom_label(aes(label = rtg), size = 8) +
  labs(title = "Average QB Rating 02'-21'",
       
       y = "Quartback Rating",
       x = "Round Drafted") +
  theme(legend.position = "none",
        plot.title=element_text(size = 10),
        plot.subtitle=element_text(size = 9),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        axis.text = element_text(size = 10)) +
  coord_flip() 
```


### This bar chart shows the average defensive ranking of quarterbacks by round drafted.

* This chart shows the average defensive ranking of quarterbacks for the first, second, and third round were the same.  The quarterbacks who were drafted in the fourth, sixth, or undrafted were only one ranking lower.

```{r defensive ranking dataframe, echo=FALSE, warning=FALSE}
defense_rank <-
qb_final %>% 
  dplyr::group_by(round_drafted) %>% 
  dplyr::summarize(across(c("defense_rank"), ~ mean(.x, na.rm = TRUE))) %>% 
  arrange(defense_rank)
```
```{r bar chart, echo=FALSE, warning=FALSE}
defense_rank %>%
  mutate(round_drafted = fct_reorder(round_drafted, defense_rank)) %>%
  mutate(across(c('defense_rank'), round, 0)) %>% 
  ggplot(aes(x = as.factor(round_drafted), y = defense_rank, fill=as.factor(round_drafted) )) +
  geom_col() + 
 
  geom_label(aes(label = defense_rank), size = 8) +
  labs(subtitle="2002-2021", 
       title= "Defense Rankings of Quarterbacks",
       y="Defense Rank (Average)", 
       x="Round Drafted")+
  theme(legend.position = "none",
        plot.title=element_text(hjust=0.5, size = 10),
        plot.subtitle=element_text(hjust=0.5, size = 9),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        axis.text = element_text(size = 10))
```

### This facet plot shows the number of different quarterbacks that participated in the Superbowl from 2002-2021.

* In this plot it shows how more quarterback from the first round participated in the last twenty Superbowls than all others combined.

```{r facet plot, echo=FALSE, warning=FALSE}
qb_final %>% 
  group_by(round_drafted, player) %>% 
  filter(superbowl =="yes") %>% 
  summarize_at(vars(rtg), list(group = mean)) %>% 
  mutate(round_drafted = str_replace(round_drafted, "1", "Round 1")) %>% 
  mutate(round_drafted = str_replace(round_drafted, "2", "Round 2")) %>%
  mutate(round_drafted = str_replace(round_drafted, "3", "Round 3")) %>%
  mutate(round_drafted = str_replace(round_drafted, "4", "Round 4")) %>%
  mutate(round_drafted = str_replace(round_drafted, "6", "Round 6")) %>%
  mutate(round_drafted = str_replace(round_drafted, "9", "Round 9")) %>% 
  #mutate(round_drafted = str_replace(round_drafted, "NA", "Undrafted")) %>% 
  ggplot(aes(x = player, y = group,  color = group))  +
  geom_point(size = 3) +
  facet_wrap(~round_drafted) +
  theme(legend.position="none",
        strip.background = element_rect(colour="black",
                                        fill="white"),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        plot.subtitle=element_text(hjust=0.5, size = 14),
        plot.title=element_text(hjust=0.5, size = 20),
  ) +
  labs(
    title= "Superbowl QBs 02'-21'",
    
    x = "Quarterbacks",
    y = "Playoff Rating (Average)")
```

### Conclusion
* The data has shown that over the twenty year period that teams with a quarterback drafted in the first round have a not only made the playoffs more, they also were more likely to make it to the Superbowl.
* The data also shows that with the exception of quarterbacks drafted in the fifth round, the average passer rating of all quarterbacks is within seven points.
* When I look at the defensive rankings based on round drafted, only quarterbacks drafted in the ninth round had a defense in the top fifteen.  Out of 32 teams most defenses were ranked in the bottom half of the league.
* Taking in the whole picture the data shows that since most quarterbacks having similar passer ratings and defensive rankings, that drafting a quarterback in the first round is a team's best chance to make the playoffs or the Superbowl.
